An Extendable \proglang{Python} Implementation of Robust Optimisation Monte Carlo

### 2022-12-31 article/article.tex
final
submitted version

\begin{table}
\begin{center}
\begin{tabular}{ c|c|c|c|c }
\hline
& \(\mu_{\theta_1}\) & \(\sigma_{\theta_1}\) & \(\mu_{\theta_2}\) & \(\sigma_{\theta_2}\) \\
\hline \hline
Rejection ABC & 0.516 & 0.142 & 0.07 & 0.172 \\
\hline
ROMC (gradient-based) & 0.501 & 0.142 & 0.033 & 0.169 \\
\hline
ROMC (Bayesian optimization) & 0.501 & 0.17 & 0.087 & 0.175 \\
\hline
ROMC (Neural Network) & 0.491 & 0.138 & 0.04 & 0.172 \\
\hline
\end{tabular}
\end{center}
\caption{Comparison of the samples obtained from the estimated
  posterior with (a) Rejection sampling and (b) the different versions
  of ROMC. We observe that the obtained samples share similar
  statistics along all methods. \label{tab:ma2}}
\end{table}

@@

The results in this paper were obtained using \proglang{Python~3.9}
with the \pkg{ELFI~0.8.4} package. The experiments have been executed
in a single machine with an \proglang{Intel® Core™ i7-8750H} Processor
an with \proglang{Ubuntu 20.04} lts operating system.

>>>>

\begin{table}
\begin{center}
\begin{tabular}{ c|c|c|c|c }
\hline
& \(\mu_{\theta_1}\) & \(\sigma_{\theta_1}\) & \(\mu_{\theta_2}\) & \(\sigma_{\theta_2}\) \\
\hline \hline
Rejection ABC & 0.516 & 0.142 & 0.07 & 0.172 \\
\hline
ROMC (gradient-based) & 0.501 & 0.142 & 0.033 & 0.169 \\
\hline
ROMC (Bayesian optimization) & 0.494 & 0.16 & 0.086 & 0.167 \\
\hline
ROMC (Neural Network) & 0.491 & 0.138 & 0.04 & 0.172 \\
\hline
\end{tabular}
\end{center}
\caption{Comparison of the samples obtained from the estimated
  posterior with (a) Rejection sampling and (b) the different versions
  of ROMC. We observe that the obtained samples share similar
  statistics along all methods. \label{tab:ma2}}
\end{table}

@@

The results in this paper were obtained using \proglang{Python~3.9},
\pkg{ELFI~0.8.4} at \proglang{Ubuntu 20.04 lts} operating system, at a
single machine with \proglang{Intel® Core™ i7-8750H} processor.
